---
title: Updates
---

```{r}
#| echo: false
#| message: false
library(sf)
library(leaflet)
Localities <- readRDS("data/Localities.rds")
```

# Statistics

Currently, **`r length(unique(Localities$bibtexkey))`** bibliographic references are processed.
You can download the list in BibTeX-format [here](data-raw/references.bib).

::: {.callout-tip}
## Further tables and figures

Further tables and figures can be included in this section to show the status quo of the database.
:::

# Geographic distribution

According to manual extraction of coordinates, this is the distribution of the studied localities.

```{r}
#| echo: false
leaflet(Localities) %>%
    addTiles(group = "osm") %>%
    addProviderTiles("OpenTopoMap", group = "topography") %>%
    addProviderTiles("Esri.WorldImagery", group = "satellite") %>%
    addCircleMarkers(radius = 5, color = "yellow", weight = 3, opacity = 0.7, fillColor = "#da1ac2", fillOpacity = 0.7, popup = ~citation) %>%
    addLayersControl(
      baseGroups = c("osm", "topography", "satellite")
    )
```
